Dynamical Properties of Molecular Gas Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-08-20 WRITEUP/ms.tex
write some more

At high redshifts, galaxies are expected to have lower metallicity, 
% stronger and harder radiation fields),
more {\sc HII} regions and ionized gas 
(given their much higher star formation rates; SFR), and 
more intense radiation stellar feedbacks.
Such differences in turn affect the thermal and chemical structures of their ISM (e.g., shielding of UV photons, heating and cooling mechanisms, and elemental abundances),
and thus, their multi-phase ISM differ from nearby galaxies.
Since \highz galaxies are the early stages of evolution of present-day galaxies, 
studying their ISM properties is essential for understanding how \SF proceed under these more extreme
conditions, thereby driving the evolution and assembly history 
of galaxies since the cosmic dark ages.
% since they set the pace for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).

@@

This paper is structured as follows.
In \Sec{sim}, we describe the setup of our simulation and the properties of our galaxy (\flower).
In \Sec{method}, we describe the method used to identify its molecular gas complexes (MC). 
In \Sec{results}, we present scaling relations found based on the properties of 
the identified MC and compare them with observations of molecular 
(sub-)structures seen in nearby and \z$>$\,0 galaxies.
In \Sec{diss}, we discuss the results and implication of our findings,
and conclude in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities 
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, 
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, 
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

% ------------------
\section{Simulations} \label{sec:sim}

@@

\section{Method} \label{sec:method}

@@

In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6\,$-$\,15, {\bf Pallo, check this pls}).
We note that this process is in essence similar to 
identifying molecular structures based on the noise levels of surface density maps 
observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
as commonly adopted in observational studies (e.g., identifying 
``clumps'' based on/after applying $\sigma$-clipping, 
using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, 
and \ncode{cprops}; \citealt{Williams94a, Rosolowsky06a}).

\begin{figure}[htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}  
\caption{
Volumetric H$_2$ density distribution of \flower taken from a single snapshot.
\label{fig:h2density}}
\end{figure}

@@

In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower 
for a given snapshot which includes contributions from its surrounding 7\,kpc.
In \Fig{MC}, we show an example of
the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{
Based on 10$^n$, where $n$ represents the 10 elements that are 
uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of 
$n_{\rm cut}$ adopted and find no significant differences 
affecting the results and conclusions of this work (see \Sec{ncut}).}
to the same snapshot as that 
used to plot \Fig{h2density}.
Since the molecular structures identified could 
easily appear as overlapping structures depending on the viewing angle, we 
also plot them in different three-dimensional projections --- so that one can more 
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots, spaced by $\Delta t$\eq50\,Myr. 
{\bf TODO: 0.1\,Myr (500 snapshots at $z$\eq9)}
Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we 
impose an addition constraint such that an identified structure only survives if it
spans at least 10 cells in 3D position-position-position (PPP) space. 
We caution that one caveats of such constraint is that 
we can only examine the parameter space of ``cloud'' scaling
relations at ``cloud'' size $R\gtrsim100$\,pc.

% --------------------
\section{Star Formation History and Cloud Evolution} \label{sec:sfh}

One of the advantage of studying the dynamical properties of molecular structures at 
$z$\ssim6 in simulation is the fact that we can examine how their properties evolve 
as a function of time. 
Especially at early epochs, where the densest structures are beginning to form; 
gas is constantly being accreted onto the central galaxy from the cosmic web and 
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding 
galaxies can disrupt the main disk and arms, likely leading to different dynamical states 
for the molecular structures (e.g., some may disperse, some may agglomerate into more massive 
structures). % mainly expecting differences in alpha_vir, sigma, M_cl.

We show the \SF history of \flower in \Fig{SFH}, where 
the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
The SFR plotted in Figure 2 of \citet{Pallottini17b}
is a factor of two higher than shown here since they also include contributions from 
massive satellites galaxies within the surrounding xxx\,kpc.}
as it evolves from an actively accreting phase to 
a starburst phase after a major merger and then back to a relatively quiescent phase
over the few hundred Myr simulated in our simulation.
The SFR of \flower is calculated based on existing young stellar population, which is 
defined to have an age of $t_{\rm age}<$\,10\,Myr.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 23, clip, width=0.45\textwidth]{\figpath/snapshot28_SFR_4Myr.png}  
\caption{
Star formation history of \flower.
\label{fig:SFH}}
\end{figure*}

\begin{figure}[htbp]
\centering
\includegraphics[trim=120 0 0 0, clip, width=0.55\textwidth]{\figpath/star_16.png}  
\\ [-5em]
\includegraphics[trim=120 0  0 0, clip, width=0.55\textwidth]{\figpath/star_27.png}  
\caption{
Projected stellar mass distribution of \flower during one of its accretion phases 
at an early stage of its evolution (top) and during one of its major starburst phases 
after a major merger (bottom).
\label{fig:phases}}
\end{figure}

\section{Cloud scaling relations} \label{sec:results}
Upon identified the molecular structures, we extract parameters such as
the virial parameter ($\alpha_{\rm vir}$), 
the cloud mass ($M_{\rm cl}$), 
the Mach number ($\mathcal{M}$), 
the velocity dispersion ($\sigma_v$), and the 
gas surface density ($\Sigma_{\rm gas}$)
to describe/characterize their dynamics.
We find that the thermal sound speed ($c_s$) 
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities.
We find comparable velocity dispersion derived by taking the root mean square ($\sigma_v^{\rm rms}$) versus
that derived using thermal and non-thermal pressure ($\sigma_v^{P+P_{\rm nt}}$), indicating that 
rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion (i.e., $\sigma_v$\eq$\sigma_v^{\rm rms}$).

\subsection{Single snapshots}  \label{sec:singless}
In each snapshot (see \Fig{MC} for example), 
we identify a set of MCs with consistently high turbulences and surface densities 
regardless of the H$_2$ density cuts adopted. 
These are the MCs at the center of the main disk of \flower.
Their high velocity dispersions and surface densities are expected since 
they are located in the nuclear regions of the 
galaxy, where the potential well is also deeper.

As we increase the density threshold, some of the MC within the main disk break 
into multiple sub-MCs.
As such, we effectively identify a population of denser molecular structures. 
This population of sub-MCs has dynamics largely
similar to those observed 
in $z$\ssim2 spatially resolved studies of gas-rich SFGs, in
terms of their velocity dispersions, sizes, and gas surface densities \citep[e.g.,][]{Swinbank11a}.

We also identify MCs in the satellite galaxies of \flower. These MCs 
tend to have lower virial parameters compared to the (sub-)MCs in the main disk of \flower, 
with $\alpha_{\rm vir}\simeq$1.
Given their low $\alpha_{\rm vir}$ parameter,
these structures are likely collapsing structures (\Fig{alpha16}).

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}  
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}  
\caption{
Larson's relation of \flower in 
accreting phase (top) and
starburst phase(bottom) and 
those observed in nearby and the \z$\sim$2 star-forming galaxy.
\label{fig:larsons_single}}
\end{figure*}

@@

\subsection{Variation in MC Properties Depending on Choice of Density Cuts}	 \label{sec:ncut}
% single Snapshot
We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites 
to test 
the robustness of our results against the choice of density threshold in \Sec{ncut}.
That is, how sensitive are the structure properties, and thus, the conclusion of our study
dependent on the choice of density thresholds.
We vary the choice of H$_2$ density for each of the snapshots and 
find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 
MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of 
cloud scaling relations).
We interpret this lack of variation a manifestation of ..., and that, at least on the scales studied here, the cloud properties are what we found ... 
Our results is therefore robust, haha.

@@

\subsection{Schmidt-Kennicutt Relation}
As benchmarking, we check the SK relation using the SFR and gas surface densities of the clouds. {\bf remind Pallo to look into this}.

\subsection{SFR-Mach Relation}
In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular 
complexes identified. 
We find a positive correlation between the two quantities, with a Pearson-$R$ coefficient of xxx, 
which is unsurprising given that our simulations include the effect of stellar feedback. That is, 
the high $\mathcal{M}$ can be interpreted as a result of \SF resulting from feedback from 
massive stars.

\subsection{Clump Mass Function}

@@

Noisy due to resolution effect, since we only have one galaxy here. However, 
we could improve the ``signal-to-noise'' ratio by including clouds identified from different 
snapshots (valid unless in some snapshots, the galaxy experience a violent event).
We find a shallower slope in the CMF of \flower (\Fig{cmf}) 
compared to those observed in nearby galaxies (based on a sample of 
$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}).

While our result, of particular relevance here is the slope of the CMF, is subject 
to the uncertainties in the analysis method and the resolution of our simulation --- i.e., that is 
we are likely biased to finding more massive clouds.
High resolution simulations will be useful to shed light on 
the evolving dynamical properties of the lower-mass molecular structures in 
galaxies at EoR; however, they are more expensive to run.
On the contrary, an advantage of using cosmological zoom-in simulations for this study
is that our computational boxes are not closed, allowing us to examine how 
the molecular complexes' properties vary under the influence of gas inflow/outflow.

\section{Mass Scales set by Toomre and Jeans Instabilities}

In the limit of a thin rotating disk, rotation can help stabilizes self-gravitational contraction for wavelengths greater than the Toomre length:
\begin{equation}
\lambda_T = 4\pi^2 G\Sigma/\kappa^2,
\end{equation} 
where $\kappa$ is the epicyclic frequency (\citealt{Toomre64a}).
However, if the condition $Q<Q_{\rm crit}$ is satisfied, where the latter is set by 
the thermal pressure, then fragmentation can happen 
(e.g., instability impose by angular momentum from gas accretion from the cosmic web and 
satellite galaxies and stellar feedback).

@@

\subsection{Larson's Relation}
The Larson's relation... empirically-motivated.

>>>>

At high redshifts, galaxies are expected to have lower metallicity, 
% stronger and harder radiation fields),
more \ion{H}{2} regions and ionized gas 
(given their much higher star formation rates; SFR), and 
more intense radiation stellar feedbacks.
Such differences in turn affect the thermal and chemical structures of their ISM (e.g., shielding of UV photons, heating and cooling mechanisms, and elemental abundances),
and thus, their multi-phase ISM differ from nearby galaxies.
Since \highz galaxies are the early stages of evolution of present-day galaxies, 
studying their ISM properties is essential for understanding how \SF proceed under these more extreme
conditions, thereby driving the evolution and assembly history 
of galaxies since the cosmic dark ages.
% since they set the pace for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).

@@

This paper is structured as follows.
In \Sec{sim}, we describe the setup of our simulation and the properties of our galaxy (\flower),
and describe the method used to identify its molecular gas complexes (MC). 
In \Sec{results}, we present scaling relations based on 
the MC identified and compare them with observations of molecular 
(sub-)structures seen in nearby and \z$>$\,0 galaxies.
We present Toomre stability analysis in \Sec{Q} and 
the cumulative mass distribution of the MCs in \flower in \Sec{cmf}.
In \Sec{diss}, we discuss the results and implications of our findings,
and present our conclusions in \Sec{conclusion}.
Throughout this paper, we adopt a concordance cosmology, with total matter, vacuum and baryonic densities 
in units of the critical density $\Omega_{\Lambda}$\eq0.692, $\Omega_m$\eq0.308, $\Omega_b$\eq0.0481, 
Hubble constant $H_0$\eq100\,$h$\,km s\pmOne\,Mpc\pmOne with $h$\eq0.678, 
spectral index $n$\eq0.967 and $\sigma_8$\eq0.826 \citep{Planck14a}.

% ------------------
\section{Method: Simulation and ``Clump''-finding} \label{sec:sim}

@@

\subsection{``Clump''-finding} \label{sec:method}

@@

In the ``clump-finding'' process, we employ a set of different density thresholds defined based on the
molecular hydrogen density of \flower taken at different cosmic times (between $z$\eq6.0\,$-$\,7.2).
We note that this process is in essence similar to 
identifying molecular structures based on the noise levels of surface density maps 
observers obtain with telescopes, using molecular line tracers such as CO, CS, and HCN,
as commonly adopted in observational studies (e.g., identifying 
``clumps'' based on/after applying $\sigma$-clipping, 
using tools such as \ncode{aips}'s task \ncode{serch}, \ncode{clumpfind}, 
and \ncode{cprops}; \citealt{Williams94a, Oka01a, Rosolowsky06a}).

\begin{figure}[Htbp]
\centering
\includegraphics[trim=35 0 10 35, clip, width=0.55\textwidth]{\figpath/hist_test_16.pdf}  
\caption{
Volumetric H$_2$ density distribution of \flower taken from a single snapshot.
\label{fig:h2density}}
\end{figure}

@@

In \Fig{h2density}, we show an example of the volumetric H$_2$ density distribution of \flower 
for a given snapshot which includes contributions from its surrounding 7\,kpc.
In \Fig{MC}, we show an example of
the molecular structures identified by applying volumetric H$_2$ density cuts of 
$n_{\rm cut}$\eq[0.32, 0.53, 0.88, 1.45, 2.45, 4.08, 6.81, 11.36, 19.00, 31.62]\,cm$^{-3}$\footnote{
Based on 10$^n$, where $n$ represents the 10 elements that are 
uniformly spaced between [$-0.5, 1.5$] in linear space.
We also vary the range of 
$n_{\rm cut}$ adopted and find no significant differences 
affecting the results and conclusions of this work except in the slope of the CMF (see \Sec{ncut} and \Sec{cmf}).}
to the same snapshot as that 
used to plot \Fig{h2density}.
Since the molecular structures identified could 
easily appear as overlapping structures depending on the viewing angle, we 
also plot them in different three-dimensional projections --- so that one can more 
easily see that they are collections of disjoint structures.
We repeat this identification process for 14 snapshots between 
redshift \z$\in$[6.0, 7.2], spaced by $\Delta t$\eq50\,Myr. 
% {\bf TODO: 0.1\,Myr (500 snapshots at $z$\eq9)}

Limited by the spatial resolution of our simulation ($l_{\rm cell}\simeq$\,30\,pc), we 
impose an addition constraint such that an identified structure only survives if it
spans at least 10 cells in 3D position-position-position (PPP) space. 
We caution that one caveats of such constraint is that 
we can only examine the parameter space of ``cloud'' scaling
relations at ``cloud'' size $R\gtrsim100$\,pc.

% --------------------
\section{Results}     \label{sec:results}
\subsection{Star Formation History and Cloud Evolution} \label{sec:sfh}

One of the advantages in studying the properties of MCs at 
$z$\ssim6 using simulations is that we can examine how their properties evolve 
as a function of time. 
This is advantageous especially at early cosmic epochs, 
when the densest structures are beginning to form; 
gas is constantly being accreted onto the central galaxy from the cosmic web and 
satellite galaxies, thereby leading to bursts of \SF.
Meanwhile, tidal forces resulting from interactions with these surrounding 
galaxies can disrupt the main disk and arms, likely leading to different dynamical states 
for the molecular structures (e.g., some may disperse while others may agglomerate into more massive 
structures). % mainly expecting differences in alpha_vir, sigma, M_cl.

We show the \SF history of \flower in \Fig{SFH}, where 
the SFR of \flower varies between $\sim$30$-$80\,\Msun\,yr\pmOne\footnote{
The SFR plotted in Figure 2 of \citet{Pallottini17b}
is a factor of two higher than shown here since they also include contributions from 
massive satellites galaxies within the surrounding $\approx$50\,kpc, which 
are accreted onto \flower at \z$\lesssim$\,2.}
as it evolves from an actively accreting phase to 
a starburst phase after a major merger and then back to a relatively quiescent phase
over the few hundred Myr simulated in our simulation.
The SFR of \flower is calculated based on existing young stellar population, which is 
defined to have an age of $t_{\rm age}<$\,10\,Myr.

@@

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 23, clip, width=0.45\textwidth]{\figpath/snapshot28_SFR_4Myr.png}  
\caption{
Star formation history of \flower.
% f_gas history? 
\label{fig:SFH}}
\end{figure*}

\begin{figure}[htbp]
\centering
\includegraphics[trim=120 0 0 0, clip, width=0.55\textwidth]{\figpath/star_16.png}  
\\ [-5em]
\includegraphics[trim=120 0  0 0, clip, width=0.55\textwidth]{\figpath/star_27.png}  
\caption{
Projected stellar mass distribution of \flower during the accretion phase
in its early stage of evolution (top) and during a major starburst phase 
after a major merger (bottom).
\label{fig:phases}}
\end{figure}

\subsection{Cloud Scaling Relations} 
Molecular clouds are the natal place for \SF, and thus,
their structure and dynamics hold important clues to understanding 
the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract parameters such as
the virial parameter ($\alpha_{\rm vir}$), 
the ``cloud'' mass ($M_{\rm cl}$), 
the ``cloud'' size ($R$),  
the Mach number ($\mathcal{M}$), 
the velocity dispersion ($\sigma$), and the 
gas surface density ($\Sigma_{\rm gas}$)
to describe/characterize their dynamics.
We show in \Fig{} the MC distributions in terms of their 
molecular gas mass, radius, gas mass fraction ($f_{\rm gas}$\eq$M_{\rm gas}$/($M_{\rm gas}$ + 
$M_*$)). 
% plt.hist($M_{\rm cl}$), color by two different mass range.. ~2E7?
% plt.hist($R_{\rm cl}$), using same color scheme
% for f_gas, same color scheme
We note that the distributions vary for different snapshots, depending on
the gas surface density, the morphology, and the evolutionary stage of \flower.
The highest surface density threshold of $n_{\rm cut}$ yields a ``minimum'' MC mass on
the order of 10$^{6.5}$\,\Msun for the densest MC identified.
Gas mass fractions of the MCs vary between $f_{\rm gas}\approx$xxx$-$0.xx. 
% which may determine the ``cloud'' mass if these MCs are formed due to gravitational 
% instabilities. We show gas fraction as a function of ``cloud'' mass in \Fig{}.
We find $\sim$10$-$13 MCs with masses exceeding 10$^8$\,\Msun across all the 
snapshots for each of the given $n_{\rm cut}$ (see \Sec{method}).

We find that the local sound speed ($c_s$) 
of all identified molecular complexes are generally much smaller compared to the their
turbulent velocities.
We find comparable velocity dispersion derived by taking the root mean square ($\sigma^{\rm rms}$) versus
that derived using thermal and non-thermal pressure ($\sigma^{P+P_{\rm nt}}$), indicating that 
rotation velocity is unlikely to be the dominant source entering the velocity dispersion reported here.
In the subsequent sections, we adopt the root mean square of the velocity field
as the velocity dispersion (i.e., $\sigma$\eq$\sigma^{\rm rms}$).
In \Sec{Q}, we also measure the contributions to the extracted velocity dispersions of the 
MCs due to galactic rotation and shear.

In the following subsections, 
we examine the MC properties in the context of the Larson's relations \citep{Larson81a}, which 
describe interactions between gravity and turbulence and is one of the ``fundamental''/first 
relations for studying star-forming molecular structure formation (linewidth-size, 
density-size, and mass-size relations) and for comparing properties of molecular structures
in different galactic environments.
In particular, the Larson's relations attempt to understand the physics behind molecular 
structures via observables (e.g., $\sigma$, $R$, and $M_{\rm cl}$).
% Inner MW: R=2-8.5 kpc, most of the mass in the molecular ISM is in the form of GMCs with sizes $gtrsim$20\,pc and masses greater than 10$^5$\,\Msun \citep{Sanders85a}.
Observations of nearby gas-rich galaxies such as M64 and NGC\,253 
show higher velocity dispersions compared 
to the disk/mid-plane of the Milky Way which 
are more consistent with those observed in the inner regions of 
Milky Way \citep{Oka01a, Rosolowsky05a, Heyer09a, Leroy15a}.  % also higher $P_{\rm int}$, 
% which is $\propto\rho\sigma^2$
While the velocity dispersions of the clouds in these nearby gas-rich galaxies are comparable
to the inner regions of Milky Way, they are found to be bigger in size (approximately 
an order of magnitude) and mass (approximately two orders of magnitude).
These bigger clouds have been interpreted as a results of their higher gas mass fractions and 
surface densities and velocity dispersions, since 
fragmentation occurs near the Jeans length $L_J\propto\sigma^2/\Sigma$ 
and Jeans mass $M_J\propto\sigma^4/\Sigma$
for dispersion-supported structures.

% Relating Larson's law to stability and pressure (perhaps move this to other section?).
A spherically symmetric cloud of mass $M$ and radius $R$ embedded within 
a medium of pressure $P$ is described using the virial theorem
\begin{equation}
\frac{1}{2}\ddot I = 2(T - T_s) + W + B,
\end{equation}
where $\ddot I$ is the second time derivative of the Lagrangian moment of inertia,
$T$ is the volume term of the total kinetic energy (including thermal and 
bulk motions), $T_s$ is the surface term due to external thermal pressure, 
$W$ is the gravity term, and $B$ is the magnetic term.
In the case where magnetic field is excluded (i.e., $B$\eq0), we can express this in terms of:
\begin{equation}
\frac{1}{2}\ddot I = 3 M \sigma^2 - \frac{\Gamma GM^2}{R} - 4\pi P_{\rm ext} R,
\label{eqn:virial}
\end{equation}
where the first term on the right hand side (RHS) is the pressure from velocity dispersion, second 
term is the gravity term, and the third term is the external pressure term.
For the case of simple virial equilibrium (SVE; i.e., equilibrium state without external pressure), 
the LHS vanishes and the equation becomes:
\begin{equation}
\alpha_{\rm vir} = \frac{3\sigma^2}{\Gamma GM/R} = \frac{5\sigma^2R}{GM},
\end{equation}
where $\Gamma$ is set to 3/5 for a uniform sphere, and we can define
\begin{equation}
V_0^2\equiv\frac{\sigma^2}{R},
\end{equation}
which is related to the scaling in one of the Larson's relations (linewidth-size), 
and can re-written in the form of: 
\begin{equation}
\sigma^2/R = \pi G \Sigma/5.
\end{equation}
For pressure-bounded virial equilibrium (PVE; i.e. equilibrium state with pressure), Equation~\ref{eqn:virial} becomes 
\begin{equation}
P_{\rm ext} = \frac{3\sigma^2M}{4\pi R^3} - \frac{\Gamma G M^2}{4\pi R^4},
\label{eqn:pext}
\end{equation}
which describes the external pressure needed to confine the gas inside a volume $V$.
Rearranging the equation and substituting $\Sigma$\eq$M/\pi R^2$, we can express 
this equation using the following:
\begin{equation}
\frac{\sigma^2}{R} = \frac{1}{3}\left(\frac{4P_{\rm ext}}{\Sigma} + \Gamma G \Sigma \pi \right).
\label{eqn:v0}
\end{equation}
For a virialized cloud, one expects a one-to-one mapping between $V_0^2$ and $\Sigma$ since
$\sigma^2/R\propto\Sigma$, whereas 
Equation~\ref{eqn:v0} represents the loci along which external pressures $P_{\rm ext}$ are 
needed in order for MCs to have linewidths $\sigma$ for a given set of surface densities. 
In other words, a cloud with $\sigma$ and $\Sigma$ offset from $\sigma^2/R\rightarrowtail\Sigma$ 
is in equilibrium with the external pressure (and therefore $V_0^2$ is not constant with $\Sigma$ but
varies depending on $P_{\rm ext}$; cf. expectation for SVE
$\sigma\propto R^{0.5}$; see e.g., \citealt{Heyer09a, Hughes10a, Hughes13b, Meidt13a}).

\subsubsection{Single Snapshots: Larson's Relations and Virial Parameter}  \label{sec:singless}

In each snapshot (see \Fig{MC} for example), 
we identify a set of MCs with consistently high turbulences and surface densities 
regardless of the choice of H$_2$ density threshold ($n_{\rm cut}$) adopted.
These are the MCs at the center of the main disk of \flower and 
occupy the top right corner of the Larson's relation shown in \Fig{larsons_single}.
Their high velocity dispersions and surface densities are expected since 
they are located in the nuclear regions of the 
galaxy, where the potential well is also deeper. The higher velocity dispersions 
in these MCs can also be understood as they have experienced more recent episodes 
of \SF as \flower is assembling its stellar mass (they also have higher stellar-to-gas mass ratios of $\sim$60). 
In fact, by $z\simeq$7.2 (i.e., the snapshot corresponding
to the top panel of \Fig{phases} and \Fig{larsons_single}), \flower has assembled 
a stellar mass of $M_*$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion 
is due in part to the stronger stellar feedback compared to e.g., MCs in its satellite galaxies.
The virial parameter of the MC identified in (the densest region of) the main disk of \flower 
indicate that the MC itself is gravitationally unbound.

As we increase the density threshold, some of the MC within the main disk break 
into multiple sub-MCs.
As such, we effectively identify a population of denser molecular structures (\Fig{MC}). 
This population of sub-MCs has dynamics largely
similar to those observed 
in $z$\ssim2 spatially resolved studies of gas-rich SFGs, in
terms of their velocity dispersions, sizes, and gas surface densities (\Fig{larsons_single}; see 
e.g., \citealt{Swinbank11a}),
with cloud sizes on the order of $R\simeq$100\,pc and velocity 
dispersions of $\sigma\simeq$\,20$-$\,80\,\kms. Their $\alpha_{\rm vir}$ 
are lower than their ``parent'' MCs in the main disk of \flower. This is consistent with
the conventional wisdom that collapsing structures result from local gravitational 
instability within globally stable structures, which are supported by 
turbulence and rotation on large scales.

We also identify MCs in the satellite galaxies of \flower. These MCs 
tend to have lower velocity dispersions compared to those of \flower which are more comparable
to those observed in the inner Milky way and 
nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), 
along the locus of $\sigma\propto R^{0.56}$.
These MCs in the satellite galaxies also have 
lower virial parameters compared to the (sub-)MCs in the main disk of \flower, 
with $\alpha_{\rm vir}\simeq$1 (see top panels of \Fig{alpha16} and \Fig{alpha27}).
Differences in their $\alpha_{\rm vir}$ most likely result from the weaker 
stellar feedback in the satellite galaxies as they have experienced less episodes of \SF compared to
\flower (i.e., lower stellar-to-gas mass ratios of $\sim$0.1). Given their low $\alpha_{\rm vir}$ parameter,
these structures are likely collapsing structures. 
Based on the $\sigma^2/R - \Sigma$ relation and the virial parameter, 
the MCs of the satellite galaxies of 
\flower are close to being in virial equilibrium
and are not supported against collapse by external pressure. % are bound

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss16_larsons.png}  
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/ss27_larsons.png}  
\caption{
Larson's (linewidth-size) relation of \flower in 
accreting phase (top) and
starburst phase(bottom) and 
those observed in nearby and the \z$\sim$2 star-forming galaxy.
\label{fig:larsons_single}}
\end{figure*}

@@

% -------------- all snapshots -----------

@@

% \subsubsection{Single Snapshots: Size Mass Relation} to merge with section 3.2.1

\subsubsection{Single Snapshots: SFR-Mach-$\alpha_{\rm vir}$ Relation}
%M~ 30 in normal spirals \citep{McKee99a}
%M~ 100 in SBs \citep{Downes98a}
In \Fig{}, we show the relation between SFR and the Mach number ($\mathcal{M}$) for the molecular 
complexes identified. 
We find a positive correlation between the two quantities, with a Pearson-$R$ coefficient of xxx, 
which is unsurprising given that our simulations include the effect of stellar feedback. That is, 
the high $\mathcal{M}$ can be interpreted as a result of \SF resulting from feedback from 
massive stars.

\subsubsection{Variation in MC Properties Depending on the Choice of Density Cuts}	 \label{sec:ncut}
% single Snapshot
We investigate possible variations in the dynamics of the molecular structures of \flower and its satellites 
to test 
the robustness of our results against the choice of density threshold by adopting 
different sets of $n_{\rm cut}$ in identifying the MCs.
That is, how sensitive are the structure properties, and thus, the results presented in \Sec{singless}
dependent on the choice of density thresholds.
We vary the choice of H$_2$ density for each of the snapshots and 
find no obvious differences in our results (i.e., inferences on the dynamics of \z$\sim$\,6 
MCs in relation to those observed in nearby and \z$\sim$2 galaxies in the context of 
cloud scaling relations). 
In addition, for the densest MC in the main disk of \flower, we find that while 
its cloud size decreases as we increase $n_{\rm cut}$ --- as one would intuitively expect, 
its velocity dispersion remain 
approximately $\sigma\simeq$200\,\kms (\Fig{larsons_single}). 
This lack of variation is reassuring, in the sense that at least on the scales studied here, 
the dynamics of the MCs are not artifacts or biased by our choice of $n_{\rm cut}$.
Our results is therefore robust, haha.

@@

\section{Mass Scales set by Toomre and Jeans Instabilities}   \label{sec:Q}
For axisymmetric mode ($m$\eq0), the dispersion relation for the growth of density perturbation in a rotating turbulent disk 
of finite thickness $h$ 
is described by:
\begin{equation}
\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma^2 k^2,
\label{eqn:3Ddisp}
\end{equation}
where $k$ is the wavenumber in the disk and $\kappa$ is the epicyclic frequency (\citealt{Toomre64a}).
The first term on the RHS describes rotation support, second term describes self-gravity, and 
the third term describes pressure support.
The epicyclic frequency is defined as:
\begin{equation}
\kappa^2\equiv\frac{2\Omega}{R}\frac{d}{dR}\left(R^2\Omega\right).
\label{eqn:kappa}
\end{equation}
% \kappa\propto\Omega 
One can then define the so-called Toomre-Q parameter/criterion for stability as
\begin{equation}
Q\equiv\frac{\sigma\kappa}{\pi G \Sigma}.
\label{eqn:Q}
\end{equation}
We can then rewrite Equation~\ref{eqn:3Ddisp} in terms of 
\begin{equation}
\omega^2 = Q^2 k^2 \left(\frac{\pi G \Sigma}{\kappa}\right)^2 - 2\pi G \Sigma |k| + \kappa^2.
\end{equation}
Thus, for $Q\lesssim$1, disk is unstable for some $k$ ($\omega^2 < 0$)
and fragmentation can happen 
(e.g., instability impose by angular momentum from gas accretion from the cosmic web and 
satellite galaxies and stellar feedback).
That is, local fragmentation takes place when gravity overcomes pressure support
from turbulence (thermal is small here) and shearing of differential rotation.

In the limit of a thin rotating disk, rotation can help stabilizes 
self-gravitational contraction for wavelengths greater than the Toomre length:
\begin{equation}
\lambda_T = 4\pi^2 G\Sigma/\kappa^2,
\end{equation} 
yielding a characteristic mass of $M_T$\eq$\frac{\pi}{4}{\lambda_T^2}{\Sigma}$\eq4$\pi^2\frac{G^2\Sigma^3}{\kappa^4}$,
which is the ``upper limit'' to which MCs can form in a shearing disk.

\section{Cumulative Mass Distribution}   \label{sec:cmf}

@@

Consistent with the mass range observed in \z$\sim$2 galaxies in $i$-band light (rest-frame visible), 
between $M_{\rm cl}\approx$10$^{7-9}$\,\Msun \citep{Elmegreen07a, Elmegreen09a}.

% slope
Noisy due to resolution effect, since we only have one galaxy here. However, 
we could improve the ``signal-to-noise'' ratio by including clouds identified from different 
snapshots\footnote{This approach is valid unless in some snapshots, 
the galaxy experience a violent event, which is relatively rare across the few 100\,Myr studied here.}.
We find a shallower slope in the CMF of \flower (\Fig{cmf}) 
compared to those observed in nearby galaxies (based on a sample of 
$\sim$70 resolved GMCs in M31, M33, IC10 and the Magellanic Clouds; \citealt{Blitz07a}).
The slope varies from $-$0.49\pmm0.01 to $-$1.17\pmm0.06 for MCs identified using the lowest and the 
highest $n_{\rm cut}$ adopted in this study.
The uncertainties here are the formal fitting uncertainties.

% interpretation
A higher $\sigma$ and $\Sigma_{\rm gas}$ is related to the higher 
pressure. The higher $\Sigma_{\rm gas}$ is also related to more massive clouds being formed.
In M64, there are few clouds with masses $M_{\rm cl}>$10$^7$\,\Msun, such massive molecular 
structures are unknown to local group, and are likely the ... from which massive clusters or OB associations are to be formed.
In CMZ, we have seen molecular clouds with high pressures $P/k_B > $10$^7$\,K\,cm$^{-3}$.

% a bit on caveat
While our result, of particular relevance here is the slope of the CMF, is subject 
to the uncertainties in the analysis method and the resolution of our simulation --- i.e., that is 
we are likely biased to finding more massive clouds.
High resolution simulations will be useful to shed light on 
the evolving dynamical properties of the lower-mass molecular structures in 
galaxies at EoR; however, they are more expensive to run.
On the contrary, an advantage of using cosmological zoom-in simulations for this study
is that our computational boxes are not closed, allowing us to examine how 
the molecular complexes' properties vary under the influence of gas inflow/outflow.

@@
